---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
library(magick)
```

```{css}
body {
  font-family: Arial;
  background: lightblue;
}
h2 {
  color: Black;
}
```

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTi4w0Il1rmXgdfBpzRxsB6LBiA3gY0HMHg-0JHRQC9Uw7ZCkXe_Kr7KEuT-1GKAQ-NQJxsw2V8CiTn/pub?gid=1435256090&single=true&output=csv")

# Renaming variables
latest_data <- logged_data %>%
  rename(
    category = 2,
    enjoy = 3, 
    rating = 4, 
    watch_time = 5,
    full_video = 6
  )
```

## YouTube Viewing Habits Analysis

This report explores YouTube viewing behavior, which focuses on categories and ratings. The aim of this report is to understand how users engage with different type of content/what type of videos they watch.

```{r}

# Summary values
max_watch <- max(latest_data$watch_time)
mean_rate <- mean(latest_data$rating)


```

::: dynamic-comment
The max watch time is `r max_watch`(minutes) and the mean rating for these videos combined are `r mean_rate` stars
:::

```{r}

ggplot(data = latest_data) + 
  geom_bar(aes(x = category, fill = category)) +
  labs(
    title = "Video Categories by Watching Mode",
    subtitle = "Displays the number of videos in each category"
  ) +
  theme_minimal()

```

As we can see in this plot of categories "Gaming" is the most dominate category and after that is learning, we can see that I like to game and learn.

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x=rating),
           fill = "yellow") +
  labs(title="Distrubution of video ratings",
       subtitle = "Shows how frequently each rating score occurs") +
  theme_minimal()
```

From what we can see here there are same amount of ratings as for 4 stars and 5 stars this can indicate that the user liked majority of the videos they watched.
With the lowest being 2 videos with 1 star and 6 videos being in 4 star and 5 star.

